Title

### 2017-05-09 paper/paper.tex
Minor changes to captioning on yahoo figure

\begin{figure*}
\includegraphics[width=\textwidth]{yahoo-interval-chaining.png}
\caption{\emph{Performance metrics of the logistic-regression based interval-chaining algorithm with $3$ clusters over 10,000 iterations. Shown on the left is a graph depicting the performance of the learning algorithm vs that of the `best' player, whose picked article is clicked by the user in every round. The regret is simply the difference in the cumulative number of successes between the two. In practice, this is an unfair comparison to make, as it is unreasonable to expect that the user would click the featured article every visit - and our results stand even stronger in comparison. On the right is a graph denoting the cumulative fraction of successful picks by the algorithm vs. the baseline (randomly selecting one out of the three pools at each step).} \label{fig:yahoo}}
\end{figure*}

>>>>

\begin{figure*}
\includegraphics[width=\textwidth]{yahoo-interval-chaining.png}
\caption{\emph{Performance metrics of the logistic-regression based interval-chaining algorithm with $3$ clusters over 10,000 iterations. Shown on the left is a graph depicting the performance of the learning algorithm vs that of the `best' player, whose picked article is clicked by the user in every round. The regret is simply the difference in the cumulative number of successes between the two. In practice, this is an unfair comparison to make, as it is unreasonable to expect that the user would click the featured article every visit - and our results stand even stronger in comparison. On the right is a graph denoting the cumulative fraction of successful picks by the algorithm vs. the baseline (randomly selecting one out of the three pools at each step). The learning algorithm appears to converge to approximately $50\%$ accuracy, which is considerably higher than the baseline.} \label{fig:yahoo}}
\end{figure*}
